Bee brain size is positively associated with urban lifestyles but not with positive population trends

### 2022-10-26 Manuscript/Ms.Rmd
Reorganising files

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.align="center", fig.height=12, fig.width=12, fig.cap="\\textbf{Figure 1.} Maps showing the location of the downloaded GBIF occurrences for the different bee species."}

>>>>

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.align="center", fig.height=12, fig.width=12, fig.cap="\\textbf{Figure 1.} Maps showing the location of the downloaded GBIF occurrences for the different bee species (N = 100). A) Selected North European countries that had a high number of records for the selected species. B) Selected states from"}
